Fast, Scalable Phrase-Based SMT Decoding

### 2016-06-09 acl.2016/acl2016.tex
bool -> size_t. Prevent segfault when using mempool

Standard Moses phrase-based configurations are used, except that we use the cube-pruning algorithm~\cite{Chiang:2007:cl} with a pop-limit of 400\footnote{\scriptsize the pop-limit was chosen following public discussion on finding a balance between decoding speed and translation quality with Moses https://www.mail-archive.com/moses-support\%40mit.edu/msg13181.html }, rather than the basic phrase-based algorithm. The cube-pruning algorithm is often employed by users who require fast decoding as it gives them the ability to trade speed with translation quality via a simple pop-limit parameter.

>>>>

Standard Moses phrase-based configurations are used, except that we use the cube-pruning algorithm~\cite{Chiang:2007:cl} with a pop-limit of 400\footnote{\scriptsize the pop-limit was chosen following public discussion on finding a balance between decoding speed and translation quality with Moses for commercial use https://www.mail-archive.com/moses-support\%40mit.edu/msg13181.html }, rather than the basic phrase-based algorithm. The cube-pruning algorithm is often employed by users who require fast decoding as it gives them the ability to trade speed with translation quality via a simple pop-limit parameter.
